Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-24 article.rnw
Add the text of the results.

@@

>>>>

\newcommand\rsquarednum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\aicnum[1]{\num{#1}}
\newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}

@@

The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
The AIC values ranged from \aicnum{\Sexpr{min(brute_data$statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$statistics$aic)}}.
\Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.
%TODO: The AIC histogram.

The ``best'' model, as indicated by AIC, was not the best with any surety; the Akaike weights indicated only a probability of only \probnum{\Sexpr{max(brute_data$statistics$aic_weight)}} that it was the best.
As such, I assessed the appropriate groupings by taking the total probability that whichever was the best model grouped a given pair of together (coclassified the pair of species).
These results are shown in \cref{fig:coclassification}.

In all, no pair of species can confidently be said to be coclassified, in the row or column groupings; no probability of coclassification exceeded \SI{60}{\percent}.
Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.

The structure of the coclassifications was very different in the row groups than in the column groups.
Most pairs of species which had a high probability of being coclassified in one grouping had a very low probability of being coclassified in the other grouping.
Only one pair of species had a relatively high probability of being coclassified in both groupings: \emph{D. pallidifrons} and \emph{D. sulfurigaster}.
Overall, more coclassification occurred in the row groupings than in the column groupings.

A high likelihood of coclassification in the row groupings was typically transitive: e.g.\ \emph{D. birchii}, \emph{D. pallidifrons} and \emph{D. sulfurigaster} each had a relatively high probability of being coclassified with one another.
More intransitivity was observed in the column groupings: \emph{D. simulans} had a relatively high probability of being coclassified with \emph{D. sulfurigaster}, and \emph{D. sulfurigaster} had a substantial probability of being coclassified with \emph{D. pallidifrons}, but \emph{D. simulans} had a much lower probability of being coclassified with \emph{D. pallidifrons}.
